Everest Bio

### 2020-11-17 index.Rmd
adding hakim

author:
  - first_name: "Mauricio"
    last_name: "Camargo"
    url: https://erpi.univ-lorraine.fr/people/Mauricio-Camargo/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0003-3867-2438 
  - first_name: "Nadège"
    last_name: "Troussier"
    url: https://recherche.utt.fr/icd-directory/nadege-troussier
    affiliation: CREIDD
    affiliation_url: https://recherche.utt.fr/icd-directory/nadege-troussier
    orcid_id: 0000-0001-6707-0300
  - first_name: "Fabio"
    last_name: "Cruz"
    url: https://erpi.univ-lorraine.fr/people/Fabio-Cruz/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0001-8529-5327
  - first_name: "Fedoua"
    last_name: "Kasmi"
    url: https://erpi.univ-lorraine.fr/people/Fedoua-Kasmi/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0001-5159-0264
  - first_name: "Pavlo"
    last_name: "Santander"
    url: http://erpi.univ-lorraine.fr/people/Pavlo-Santander/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    #orcid_id: 0000-0001-6328-1338
bibliography: library.bib
csl: journal-of-cleaner-production.csl
link-citations: yes
linkcolor: blue 
site: distill::distill_website
---

>>>>

author:
  - first_name: "Nadège"
    last_name: "Troussier"
    url: https://recherche.utt.fr/icd-directory/nadege-troussier
    affiliation: CREIDD
    affiliation_url: https://recherche.utt.fr/icd-directory/nadege-troussier
    orcid_id: 0000-0001-6707-0300
  - first_name: "Mauricio"
    last_name: "Camargo"
    url: https://erpi.univ-lorraine.fr/people/Mauricio-Camargo/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0003-3867-2438 
  - first_name: "Hakim"
    last_name: "Boudaoud"
    url: https://erpi.univ-lorraine.fr/people/Hakim-Boudaoud/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0003-4452-5952

  - first_name: "Fabio"
    last_name: "Cruz"
    url: https://erpi.univ-lorraine.fr/people/Fabio-Cruz/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0001-8529-5327
  - first_name: "Fedoua"
    last_name: "Kasmi"
    url: https://erpi.univ-lorraine.fr/people/Fedoua-Kasmi/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0001-5159-0264
  - first_name: "Pavlo"
    last_name: "Santander"
    url: http://erpi.univ-lorraine.fr/people/Pavlo-Santander/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    #orcid_id: 0000-0001-6328-1338
bibliography: library.bib
csl: journal-of-cleaner-production.csl
link-citations: yes
linkcolor: blue 
site: distill::distill_website
---
